Excerpt: Recomposition

### 2021-04-09 formalism.tex
move configs, figures, and sections to separate files

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review,anonymous,nonacm]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{POPL} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2021}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

\bibliographystyle{ACM-Reference-Format}
%\citestyle{acmauthoryear}
\citestyle{acmnumeric}

%%%%%%%%

\renewcommand{\topfraction}{1} % Allow floats to take up the page
\renewcommand{\textfraction}{0}

%%%%%%%%
% \autoref from hyperref
\renewcommand{\AMSautorefname}          {Equation}
\renewcommand{\appendixautorefname}     {Appendix}
\renewcommand{\chapterautorefname}      {Chapter}
\renewcommand{\equationautorefname}     {Equation}
\renewcommand{\FancyVerbLineautorefname}{Line}
\renewcommand{\figureautorefname}       {Figure}
\renewcommand{\footnoteautorefname}     {Footnote}
\renewcommand{\Hfootnoteautorefname}    {Footnote}
\renewcommand{\itemautorefname}         {Item}
\renewcommand{\Itemautorefname}         {Item}
\renewcommand{\pageautorefname}         {Page}
\renewcommand{\paragraphautorefname}    {Section}
\renewcommand{\partautorefname}         {Part}
\renewcommand{\sectionautorefname}      {Section}
\renewcommand{\subparagraphautorefname} {Section}
\renewcommand{\subsectionautorefname}   {Section}
\renewcommand{\subsubsectionautorefname}{Section}
\renewcommand{\tableautorefname}        {Table}
\renewcommand{\theoremautorefname}      {Theorem}

%% Packages
\usepackage{booktabs}
\usepackage[rule=false]{subcaption}
\usepackage{graphicx}
% \usepackage{semantic}
\let\colonapprox\undefined % Avoid redefinition error in `colonequals`
\let\colonsim\undefined % Avoid redefinition error in `colonequals`
\usepackage{colonequals}
% \usepackage{mathpartir}
\usepackage{stmaryrd}
\usepackage{fontawesome}
\usepackage{array}
\usepackage{todonotes}
% \usepackage[ruled]{algorithm2e}

% Load MnSymbol without clobbering \ast
% See https://tex.stackexchange.com/a/269691
\usepackage{amsmath}% needed before mathabx
\let\amsast=\ast
\usepackage[matha]{mathabx}% needed to prevent \ast getting clobbered
\let\abxast=\ast
\usepackage{MnSymbol}
\let\mnast=\ast
\let\ast=\abxast

% \selectcolormodel{gray}

\def\_{\texttt{\textunderscore}}

\newcommand{\id}[1]{\textcolor{gray}{\ensuremath{#1}}}

%%%%%%%%
% TikZ Stuff
%\usepackage{etex} % Fix "No room for new \dimen" error
\usepackage{shellesc} % Fix bug that breaks the tikz 'external' library
\usepackage{tikz}
\usetikzlibrary{babel} % Ensure compatibility the 'babel' package

\usetikzlibrary{external} % Needs to be separately enabled
%\tikzexternalize % Enable externalization
%\usepackage{lua-visual-debug}

\usetikzlibrary{arrows.meta} % Arrow Tips
\tikzset{>=Stealth}
%\tikzset{<=stealth}
%\tikzset{arrows={-Stealth[scale=50]}}
%\tikzset{edge from parent/.style={draw,->,line width=0.6pt}}
%\tikzset{wideline/.style={line width=0.7pt}}
%\tikzset{boldline/.style={color=black,line width=1.0pt}}

\usetikzlibrary{
  backgrounds,  % Provides "framed" and "gridded"
  bending,      % bending arrow tips
  decorations.pathmorphing,   % Provides wavy edges
  graphs,       % Graph *notation*
  graphdrawing, % Graph *layout*
  quotes,       % Quote syntax (e.g., "foo")
}

\usegdlibrary{
  trees,
}

\tikzset{
  %every picture/.style={framed, background rectangle/.style={draw=gray!50}},
}
\tikzset{edge style/.style={
  draw,
  %color=gray,
  font={\small\ttfamily},
  /tikz/every edge quotes/.style={
    %draw=gray!20,
    anchor=west,
    swap/.append code={
      \ifpgfarrowswap
        \pgfkeysalso{anchor=west}
      \else
        \pgfkeysalso{anchor=east}
      \fi}},
}}
\tikzset{graphs/graph style/.style={
  tree layout,
  level distance=0.5cm,
  level sep=0.5cm,
  sibling distance=0.5cm,
  sibling sep=0.1cm,
  part distance=0.1cm,
  part sep=0.1cm,
  component distance=0.1cm,
  component sep=0.1cm,
  nodes={
    draw,
    %color=gray,
    inner sep=2pt,
    rounded corners=1mm},
  edges={edge style},
}}
\tikzset{graphs/root style/.style={
 %draw=none,
 as={\textbullet$_{\id{0}}$}
}}
\tikzset{alice/.style={
  color=red!80!black,
  font={\bfseries\small},
  thick,
}}
\tikzset{bob/.style={
  color=green!60!black,
  font={\bfseries\small},
  thick,
}}
\tikzset{merge/.style={
  color=blue,
  font={\bfseries\small},
  thick,
}}
\tikzset{alice edge/.style={alice, edge style, font={\bfseries\small}}}
\tikzset{alice node/.style={alice}}
\tikzset{alice step/.style={alice}}
\tikzset{bob edge/.style={bob, edge style}, font={\bfseries\small}}
\tikzset{bob node/.style={bob}}
\tikzset{bob step/.style={bob}}
\tikzset{merge edge/.style={merge, edge style}, font={\bfseries\small}}
\tikzset{merge node/.style={merge}}
\tikzset{merge step/.style={merge,decorate,decoration={coil,amplitude=1.0pt,segment length=7.0pt,aspect=0}}}
\tikzset{star/.style={edge node={node[inner sep=0pt,at end,sloped] {\textbf{\huge${}^{\ast}$}}}}}

%%%%%%%%
% Lang components

% sets
\def\A{\mathcal{A}}
%\def\C{\mathcal{C}}
\def\E{\mathcal{E}}
\def\G{\mathcal{G}}
\def\I{\mathcal{I}}
\def\K{\mathcal{K}}
\def\P{\mathcal{P}}
\def\U{\mathcal{U}}
\def\V{\mathcal{V}}
\def\e{\varepsilon}
\def\AA{\textbf{A}}
\def\EE{\textbf{E}}

\newcommand{\abs}[1]{\left\lvert#1\right\rvert}

% constructors
\def\ExpVar{\mathsf{Exp\_var}}
\def\ExpLam{\mathsf{Exp\_lam}}
\def\ExpApp{\mathsf{Exp\_app}}
\def\ExpNum{\mathsf{Exp\_num}}
\def\ExpPlus{\mathsf{Exp\_plus}}
\def\ExpTimes{\mathsf{Exp\_times}}
\def\PatVar{\mathsf{Pat\_var}}
\def\TypNum{\mathsf{Typ\_num}}
\def\TypArrow{\mathsf{Typ\_arrow}}

% indexes
\def\Root{\mathsf{Root}}
\def\LamParam{\mathsf{Lam\_param}}
\def\LamType{\mathsf{Lam\_type}}
\def\LamBody{\mathsf{Lam\_body}}
\def\AppFun{\mathsf{App\_fun}}
\def\AppArg{\mathsf{App\_arg}}
\def\PlusLeft{\mathsf{Plus\_left}}
\def\PlusRight{\mathsf{Plus\_right}}
\def\TimesLeft{\mathsf{Times\_left}}
\def\TimesRight{\mathsf{Times\_right}}
\def\ArrowArg{\mathsf{Arrow\_arg}}
\def\ArrowResult{\mathsf{Arrow\_result}}

% actions
\def\Create{\text{Create}}
\def\Destroy{\text{Destroy}}
\def\Down{\text{Down}}
\def\Enqueue{\text{Enqueue}}
\def\Left{\text{Left}}
\def\Move{\text{Move}}
\def\Num{\text{Num}}
\def\Restore{\text{Restore}}
\def\Right{\text{Right}}
\def\Select{\text{Select}}
\def\Send{\text{Send}}
\def\Up{\text{Up}}

% relations
\DeclareMathOperator{\s}{\text{S}}
\DeclareMathOperator{\MP}{\text{MP}}
\DeclareMathOperator{\CC}{\text{C}}
\DeclareMathOperator{\D}{\text{D}}

\DeclareMathOperator{\sort}{\text{sort}}
\DeclareMathOperator{\arity}{\text{arity}}
\DeclareMathOperator{\childVertexes}{\text{childVertexes}}
\DeclareMathOperator{\cursorChildren}{\text{cursorChildren}}
\DeclareMathOperator{\vertexChildren}{\text{vertexChildren}}
\DeclareMathOperator{\dom}{\text{dom}}
\DeclareMathOperator{\edges}{\text{edges}}
\DeclareMathOperator{\known}{\text{known}}
\DeclareMathOperator{\liveEdges}{\text{liveEdges}}
\DeclareMathOperator{\liveVertexes}{\text{liveVertexes}}
\DeclareMathOperator{\multiparents}{\text{multiparents}}
\DeclareMathOperator{\orphans}{\text{orphans}}
\DeclareMathOperator{\parentVertexes}{\text{parentVertexes}}
\DeclareMathOperator{\reachable}{\text{reachable}}
\DeclareMathOperator{\seen}{\text{seen}}
\DeclareMathOperator{\unseen}{\text{unseen}}
\DeclareMathOperator{\vertexes}{\text{vertexes}}
\DeclareMathOperator{\vertex}{\text{vertex}}
\DeclareMathOperator{\publish}{\text{publish}}
\DeclareMathOperator{\leftIndex}{\text{leftIndex}}
\DeclareMathOperator{\rightIndex}{\text{rightIndex}}
\DeclareMathOperator{\downIndex}{\text{downIndex}}
\DeclareMathOperator{\defaultIndex}{\text{defaultIndex}}

% graph decomposition operators
\DeclareMathOperator{\expr}{\text{expr}}
\DeclareMathOperator{\patt}{\text{patt}}
\DeclareMathOperator{\type}{\text{type}}
\DeclareMathOperator{\parents}{\text{parents}}
\DeclareMathOperator{\ancestors}{\text{ancestors}}
\DeclareMathOperator{\vertices}{\text{vertices}}
\DeclareMathOperator{\children}{\text{children}}
\DeclareMathOperator{\lfp}{\text{lfp}}

\DeclareMathOperator{\multiParented}{\text{multiParented}}
\DeclareMathOperator{\singleParented}{\text{singleParented}}
\DeclareMathOperator{\deleted}{\text{deleted}}

% Define outline versions of + and -
\def\outlinepad{0.4pt}
\def\outlinestroke{0.4pt}
\newcommand{\Plus}{\mathord{
\begin{tikzpicture}[anchor=base, baseline]
%\node at (0,0) {+};
\path[draw, line width=\outlinestroke]
   ( 0.333em+\outlinestroke/2+\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --( 0.333em+\outlinestroke/2+\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --( 0.021em+\outlinestroke/2+\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --( 0.021em+\outlinestroke/2+\outlinepad, -0.084em-\outlinestroke/2-\outlinepad)
 --(-0.020em-\outlinestroke/2-\outlinepad, -0.084em-\outlinestroke/2-\outlinepad)
 --(-0.020em-\outlinestroke/2-\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --(-0.333em-\outlinestroke/2-\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --(-0.333em-\outlinestroke/2-\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --(-0.020em-\outlinestroke/2-\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --(-0.020em-\outlinestroke/2-\outlinepad,  0.583em+\outlinestroke/2+\outlinepad)
 --( 0.021em+\outlinestroke/2+\outlinepad,  0.583em+\outlinestroke/2+\outlinepad)
 --( 0.021em+\outlinestroke/2+\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --cycle
 ;
\end{tikzpicture}
}}
\newcommand{\Minus}{\mathord{
\begin{tikzpicture}[anchor=base, baseline]
%\node at (0,0) {$-$};
\path[draw, line width=\outlinestroke]
   ( 0.306em+\outlinestroke/2+\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --( 0.306em+\outlinestroke/2+\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --(-0.306em-\outlinestroke/2-\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --(-0.306em-\outlinestroke/2-\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --cycle
 ;
\end{tikzpicture}
}}

% custom syntax

\usepackage{xstring}

\newcommand{\hole}{\ensuremath{\square}} %\textcolor{violet}{\llparenthesis}}\textcolor{violet}{\rrparenthesis}}
\newcommand{\conflictHole}[1]{%
{\noexpandarg\StrSubstitute{#1}{,}{\textcolor{red}{\;\textbf{|}\;}}[\myargs]%
{\textcolor{red}{\textbf{\{}}\myargs\textcolor{red}{\textbf{\}}}}}}%

% Calling \newvertex{Foo}{bar} defines
%   \vidFoo to be a new id number, and
%   \vFoo to be \texttt{bar}\ensuremath{_{\vidFoo}}
\newcounter{NodeVertexCounter}
\newcommand{\newvertex}[2]{%
\ifodd\theNodeVertexCounter
  \addtocounter{NodeVertexCounter}{1}%
\else
  \addtocounter{NodeVertexCounter}{2}%
\fi
\expandafter\newcommand\csname vid#1\endcsname{}% This is just to check if this is a redefinition
\expandafter\global\expandafter\edef\csname vid#1\endcsname{\theNodeVertexCounter}%
\expandafter\newcommand\csname v#1\endcsname{}% This is just to check if this is a redefinition
\expandafter\gdef\csname v#1\endcsname{\texttt{#2}\ensuremath{_{\id{\csname vid#1\endcsname}}}}%
}
\newcommand{\newedge}[2]{%
\ifodd\theNodeVertexCounter
  \addtocounter{NodeVertexCounter}{2}%
\else
  \addtocounter{NodeVertexCounter}{1}%
\fi
\expandafter\newcommand\csname eid#1\endcsname{}% This is just to check if this is a redefinition
\expandafter\global\expandafter\edef\csname eid#1\endcsname{\theNodeVertexCounter}%
\expandafter\newcommand\csname e#1\endcsname{}% This is just to check if this is a redefinition
\expandafter\gdef\csname e#1\endcsname{\texttt{#2}\ensuremath{_{\id{\csname eid#1\endcsname}}}}%
}
\setcounter{NodeVertexCounter}{-1}
\newvertex{Root}{Root}

% Support \includegraphics of .dot files
\DeclareGraphicsRule{.dot}{pdf}{.pdf}{`dot -Tpdf #1 -o \noexpand\OutputFile}

\newcommand{\Edge}[1]{Edge~#1}
\newcommand{\Vertex}[1]{Vertex~#1}
\newcommand{\figureCode}[1]{\textbf{\texttt{#1}}\vskip1em}
\newcommand{\multiVertex}[1]{\textcolor{red}{\ensuremath{\curlyveedownarrow_{#1}}}}
\newcommand{\cycleVertex}[1]{\textcolor{red}{\ensuremath{\rcirclearrowleft_{#1}}}}
\newcommand{\orphanVertex}[1]{\textcolor{red}{\ensuremath{\mathbf{\ndownarrow_{#1}}}}}
\newcommand{\parens}[1]{\textcolor{gray}{(}#1\textcolor{gray}{)}}
\newcommand{\otherVertexVskip}{\vskip0.5em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureSimple
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\newedge{SimpleY}{R}%
\newvertex{SimpleY}{y}%
\newcommand{\figureSimple}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Simple/a) [anchor=base] {\strut};
\end{tikzpicture}
}%
\label{fig:Simple:a}
\figureCode{x * \hole{}}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style, color=black] -> {
  "\vSimpleTimes" [> "\eSimpleTimes", >color=black, color=black] -> {
   "\vSimpleX" [> "\eSimpleX"', >color=black, color=black],
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Simple/b) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Simple/a) to (-2em, 0cm |- node/Simple/b);
\end{tikzpicture}
}%
\label{fig:Simple:b}
\figureCode{x * y}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
  root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "\vSimpleY" [> "\eSimpleY", >alice edge, alice node]
  }
  }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Simple/c) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Simple/b) to (-2em, 0cm |- node/Simple/c);
\end{tikzpicture}
}%
\label{fig:Simple:c}
\figureCode{\hole{} * y}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
  root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
    {},
    "\vSimpleY" [> "\eSimpleY"]
  }
  }
};
\path (-0.25cm,-1.7cm) graph[graph style] {
  "\vSimpleX"
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Code that Includes a Hole and Some Simple Edits.}%
\label{fig:Simple}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureWrap
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{WrapPlus}{Root}
\newvertex{WrapPlus}{+}
\newedge{WrapTimes}{L}
\newcommand{\figureWrapMove}{
\begin{figure}
\centering
\begin{minipage}[t]{.45\linewidth}
\hskip0.12\columnwidth
%%%%%%%%
\begin{subfigure}[t]{0.28\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (node/Simple/cx) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Simple:c}}}};
%%%%
\path (0cm,0cm) node (node/Wrap/a) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Simple/cx) to (-2em, 0cm |- node/Wrap/a);
\end{tikzpicture}
}%
\label{fig:Wrap:a}
\figureCode{\hole{}}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (0cm,-1.7cm) graph[graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vSimpleY" [> "\eSimpleY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.28\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Wrap/b) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Wrap/a) to (-2em, 0cm |- node/Wrap/b);
\end{tikzpicture}
}%
\label{fig:Wrap:b}
\figureCode{\hole{} + \hole{}}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus", >alice edge, alice node]
 }
};
\path (0cm,-1.7cm) graph[graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vSimpleY" [> "\eSimpleY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.28\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Wrap/c) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Wrap/b) to (-2em, 0cm |- node/Wrap/c);
\end{tikzpicture}
}%
\label{fig:Wrap:c}
\figureCode{\hole{} * y + \hole{}}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eWrapTimes"', >alice edge] -> {
    {},
    "\vSimpleY" [> "\eSimpleY"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Wrapping.  (Note that this figure omits the orphaned \vSimpleX{} since it is no longer relevant to the narrative of this paper.)}%
\label{fig:Wrap}
\end{minipage}
% \end{figure}
% }
%
\hfil
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMove
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MoveTimes}{R}
% \newcommand{\figureMove}{
% \begin{figure}[H]
\begin{minipage}[t]{.45\linewidth}
\hfill
%\hskip0.12\columnwidth
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Move/a) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Wrap/c) to (-2em, 0cm |- node/Move/a);
\end{tikzpicture}
}%
\label{fig:Move:a}
\figureCode{\hole{} + \hole{}}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (0cm,-1.7cm) graph [graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vSimpleY" [> "\eSimpleY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Move/b) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Move/a) to (-2em, 0cm |- node/Move/b);
\end{tikzpicture}
}%
\label{fig:Move:b}
\figureCode{\hole{} + \hole{} * y}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes", >alice edge] -> {
    {},
    "\vSimpleY" [> "\eSimpleY"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Repositioning Code.}%
\label{fig:Move}
\end{minipage}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureDifferentParts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{DifferentPartsAlice}{L}
\newvertex{DifferentPartsAlice}{u}
\newedge{DifferentPartsBob}{R}
\newvertex{DifferentPartsBob}{v}
% \newcommand{\figureDifferentParts}{
\newcommand{\figureDifferentPartsNestedParts}{
\begin{figure}
\begin{minipage}[t]{0.45\linewidth}
%\hfill
\hskip0.12\columnwidth
%%%%%%%%
\begin{subfigure}[t]{0.28\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (node/Move/bx) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Move:b}}}};
\path (0cm,0cm) node (node/DifferentParts/a) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Move/bx) to (-2em, 0cm |- node/DifferentParts/a);
\end{tikzpicture}
}%
\label{fig:DifferentParts:a}
\figureCode{\hole{} + u * y}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
  {},
  "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentPartsAlice" [> "\eDifferentPartsAlice"', >alice edge, alice node],
    "\vSimpleY" [> "\eSimpleY"]
  }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.28\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/DifferentParts/b) [anchor=base] {\strut};
\path [draw,->,bob step] (node/Move/bx) to [out=15,in=165,star] (-2em, 0cm |- node/DifferentParts/b);
\end{tikzpicture}
}%
\label{fig:DifferentParts:b}
\figureCode{\hole{} + \hole{} * v}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
  {},
  "\vSimpleTimes" [> "\eMoveTimes"] -> {
    {},
    "\vDifferentPartsBob" [> "\eDifferentPartsBob", >bob edge, bob node]
  }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.28\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/DifferentParts/c) [anchor=base] {\strut};
\path [draw,->,merge step] (node/DifferentParts/a) to [out=15,in=165] (-2em, 0cm |- node/DifferentParts/c);
\path [draw,->,merge step] (node/DifferentParts/b) to (-2em, 0cm |- node/DifferentParts/c);
\end{tikzpicture}
}%
\label{fig:DifferentParts:c}
\figureCode{\hole{} + u * v}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
  {},
  "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentPartsAlice" [> "\eDifferentPartsAlice"', >merge edge, merge node],
    "\vDifferentPartsBob" [> "\eDifferentPartsBob", >merge edge, merge node]
  }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Users Editing Different Parts of the Code.}%
\label{fig:DifferentParts}
\end{minipage}
% \end{figure}
% }
%
\hfil
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureCommutativity
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newcommand{\figureCommutativity}{
% \begin{figure}
% \centering
% \begin{figure}
% \centering
% \begin{tikzpicture}
% \path (-3cm, 0cm) node (a) [align=center]       {Original \\ Version};
% \path ( 0cm, 1cm) node (b) [align=center,alice node] {Alice's  \\ Version};
% \path ( 0cm,-1cm) node (c) [align=center,bob node]   {Bob's    \\ Version};
% \path ( 3cm, 0cm) node (d) [align=center]       {Combined \\ Version};
% \path [draw,->,alice step] (a) -- node [pos=0.7,auto] {Alice's Edits} (b);
% \path [draw,->,bob step]   (a) -- node [pos=0.7,auto,swap]      {Bob's Edits}   (c);
% \path [draw,->,merge step] (b) -- node [pos=0.3,auto] {Sync} (d);
% \path [draw,->,merge step] (c) -- node [pos=0.3,auto,swap]      {Sync} (d);
% \end{tikzpicture}
% \caption{TODO:Commutativity}
% \label{fig:Commutativity}
% \end{figure}
% }
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureNestedParts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{NestedPartsAlice}{L}
\newvertex{NestedPartsAlice}{w}
\newedge{NestedPartsBob}{L}
% \newcommand{\figureNestedParts}{
% \begin{figure}
\begin{minipage}[t]{0.45\linewidth}
\hfill
%\hskip0.12\columnwidth
%%%%%%%%
\begin{subfigure}[t]{0.25\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/NestedParts/a) [anchor=base] {\strut};
\path [draw,->,alice step] (node/DifferentParts/c) to[star] (-2em, 0cm |- node/NestedParts/a);
\end{tikzpicture}
}%
\label{fig:NestedParts:a}
\figureCode{\hole{} + w * v}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vNestedPartsAlice" [> "\eNestedPartsAlice"', >alice edge, alice node],
    "\vDifferentPartsBob" [> "\eDifferentPartsBob"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.25\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/NestedParts/b) [anchor=base] {\strut};
\path [draw,->,bob step] (node/DifferentParts/c) to [out=15,in=165,star] (-2em, 0cm |- node/NestedParts/b);
\end{tikzpicture}
}%
\label{fig:NestedParts:b}
\figureCode{u * v + \hole{}}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedPartsBob"', >bob edge] -> {
    "\vDifferentPartsAlice" [> "\eDifferentPartsAlice"'],
    "\vDifferentPartsBob" [> "\eDifferentPartsBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.25\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/NestedParts/c) [anchor=base] {\strut};
\path [draw,->,merge step] (node/NestedParts/a) to [out=15,in=165] (-2em, 0cm |- node/NestedParts/c);
\path [draw,->,merge step] (node/NestedParts/b) to [out=15,in=165] (-2em, 0cm |- node/NestedParts/c);
\end{tikzpicture}
}%
\label{fig:NestedParts:c}
\figureCode{w * v + \hole{}}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedPartsBob"', >merge edge] -> {
    "\vNestedPartsAlice" [> "\eNestedPartsAlice"', >merge edge, merge node],
    "\vDifferentPartsBob" [> "\eDifferentPartsBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Users Editing Nested Parts of the Code.}%
\label{fig:NestedParts}
\end{minipage}
\end{figure}
}

>>>>

\documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{POPL} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2021}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

\setcopyright{none}

\input{config-tex}
\input{config-tikz}
\input{config-glyphs}
\input{config-definitions}
\input{config-graphs}
